Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-01-16 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
final draft ready for review

\documentclass[12pt]{article}

\usepackage{setspace}
\doublespacing
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}

@@

\usepackage{titlesec}
\titleformat{\subsubsection}[runin]
  {\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}

@@

%BJC5: wondering about replacing "Predicts long timescale behavior" with "predicts selectivity"
%MRS6: I would focus first on the outputs.  Not sure about the behavior/vs. selectivity.  Probably 
% selelctivity since it's more results oriented. ``of varying complexity'' is unneeded in the tite
%\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
%and Predicts Long Timescale Behavior in Nanoscale Pores.}
% BJC6: The only issue with selectivity is that I don't think it would include a timescale.
%MRS7: true, could just be ``predicting selectivity''
\title{Capturing subdiffusive solute dynamics and predicting selectivity in nanoscale pores
with time series modeling}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \graphicspath{{./figures/}}
  \maketitle

  %BJC6: I could make abstract margins smaller
  \begin{abstract}

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores. 
  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time 
  random walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore 2 variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies 2 sets of parameters based on the solute's radial distance from the
  closest pore center. Next, we generalize Markov state models, treating the
  configurational state of the system as a Markov process, each
  of which has separate transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. 
  %BJC7: added  
  However, qualitative differences between MD and simulated MSDDM trajectories
  may limit its usefulness. 
  Finally, we demonstrate how one can use our models to estimate flux of a solute
  across a macroscopic-length pore and, based on those quantities, the membrane's selectivity towards each solute.
  This work helps to connect microscopic chemically-dependent solute 
  motions and macroscopic membrane performance.

@@

@@

%  BJC4: Moved this paragraph to later
%  Mathematical descriptions of transport in complex separations membranes are 
%  a powerful way to understand mechanisms and formulate membrane design principles. 
%  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
%  The complexity of a model generally parallels the complexity of the transport 
%  mechanism at hand, as well as the transport information the model conveys.
%  In dense homogeneous membranes, the solution-diffusion model can extract 
%  diffusion and partition coefficients and has successfully predicted solute 
%  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
%  models yield predictions of diffusion coefficients and solute transport rates 
%  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
%  tracking approaches take us beyond continuum modeling and allow us to 
%  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
%  level, one can use molecular dynamics (MD) simulations to study both single 
%  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
%  All of these approaches facilitate speculation on the molecular origins of separations
%  by attempting to give a more intuitive understanding of how solutes move as a function
%  of their environment, in turn suggesting experiments that could be performed.

  Highly selective separations membranes are desirable in numerous applications. 
  The ability to efficiently separate ions from saline water sources using membranes 
  has been actively pursued for years in an effort to create potable water for people 
  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  there is a strong interest in creating breathable fabrics which selectively allow 
  passage of water vapor.~\cite{mondloch_destruction_2015}
%  The pace at which we achieve these or any other selective separation goals will be 
%  heavily influenced by the quality of insights gained by the modeling approaches above.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water present in the tail region is omitted 
  for clarity.}\label{fig:membrane_structure}
  \end{figure}

@@

  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form: 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha < 1$
  indicates a subdiffusive process, while values of $\alpha = 1$ and $\alpha > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

  %MRS6: next paragraph could be clearer.  Maybe motivate at the beginning why the importance of time. vs. ensemble averated. It's sprung a sort of a surprise there's a difference 
  %BJC6: reorganized a little and broke into paragraphs meant to convey separate ideas.
  %MRS7: definitely improved, I had a couple of comments to further refine.
  One can measure MSD in two ways. The time-averaged MSD measures all observed
  displacements over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd}
  \end{equation}
  where T is the length of the trajectory. The ensemble averaged MSD measures
  displacements with respect to a particle's initial position:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation}
  Fits to the \textit{ensemble} averaged MSD will always reproduce the form of 
  Equation~\ref{eqn:msd_form}.

@@

  We chose to analyze just the time-averaged MSD because, compared to the ensemble
  average, it is a more statistically robust measure of the average distance a 
  solute travels over time. Although theoretically possible, we do not use the 
  ensemble averaged MSD to calculate $\alpha$ because we can extract the same 
  parameter with higher precision using the dwell time distributions as described below.

%  Only the \textit{ensemble} averaged MSD will reproduce the form of 
%  Equation~\ref{eqn:msd_form} in all cases.
%  
%  We analyzed the time-averaged MSD of the simulated trajectories by measuring
%  all possible displacements over time lag $\tau$:
%  \begin{equation}
%  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
%  \end{equation}
%  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
%  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
%  MSD is given by:
%  \begin{equation}
%  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
%  \label{eqn:ensemble_msd}
%  \end{equation} 
%  In a pure CTRW, for example, the power law distribution of trapping times leads to
%  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
%  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
%  law trapping behavior, the time between hops diverges so there is no characteristic
%  measurement time scale of solute motion. In fact, as measurement time increases, the 
%  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
%  with trapping times on the order of the measurement time get incorporated into the 
%  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
%  because, compared to the ensemble average, it is a more statistically robust measure
%  of the average distance a solute travels over time. 
%  %MRS6: does it correspond properly to the physical situation of entry into the pore of new particles at each unit time?
%  Although theoretically possible, we do
%  not use the MSD to calculate $\alpha$ because we can extract the same parameter 
%  with higher precision using the dwell time distributions as described below.

%  of the process is exhibits weak ergodicity breaking due to 
%  If the underlying subdiffusive process is not ergodic, like a pure CTRW, the time
%  averaged MSD becomes linear.

@@

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete intervals dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha$ 
  parameter we calculated by maximizing the likelihood function: 
  %BJC6: I could move these MLE equations to Supporting  
  %MRS7: for PRE, can leave in.
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of	$t$.~\cite{clauset_power-law_2009}

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. 
  %We cannot observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. We do this by adding 
  an exponential cut-off to the power law so the dwell time distribution is 
  now proportional to $t^{-1 - \alpha}e^{-\lambda t}$.
  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  \subsection{Solute Flux}\label{section:mfpt}

@@

  It is computationally infeasible to simulate trajectories long enough that they
  traverse the length of a macroscopic pore. To date, the thinnest H\textsubscript{II}
  LLC membrane synthesized with the monomer in this work was 7$\mu$m thick. Using
  24 cores to simulate trajectory realizations in parallel, it takes on the order 
  of 1 day to simulate 10000 sFBMcut realizations of solutes traversing a 50 nm pore.
  The RAM requirements and performance scales greater than linearly and thus would
  take an infeasible amount of memory and time to simulate transport through a pore
  over 100 times longer. One could improve performance significantly by simulating 
  less trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting 
  Information, we determined that one can simulate as few as 100 sFBMcut realizations
  in order to parameterize Equation~\ref{eqn:flux_decay}. For better precision, we 
  recommend simulating at least 1000 realizations. Even with an order of magnitude
  decrease in number of trajectories, it is still infeasible to simulate
  experimental-length pores.

  We used simulated trajectories which traverse computationally-reasonable length
  pores in order to construct an empirical model which one can use to estimate 
  particle flux for arbitrary length pores. We fit Equation~\ref{eqn:passage_times}
  to the empirical distribution of first passage times in Figure~\ref{fig:fpt_distributions}
  and used the expected value of the analytical equation to calculate flux from 
  Equation~\ref{eqn:hill_relation}. As shown in Figures~\ref{fig:flux_curves_ad} and
  \ref{fig:flux_curves_msddm}, the flux appears to scale according to a power law 
  of the form:
  \begin{equation}
  J(L) = AL^{-\beta} 
  \label{eqn:flux_decay}
  \end{equation}

  \begin{figure}
  \centering
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{fpt_distributions.pdf}
  \caption{}\label{fig:fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{flux_curves.pdf}
  \caption{sFBMcut}\label{fig:flux_curves_ad}
  \end{subfigure}
  \caption{(a) The distributions of first passage times generated from the sFBMcut model
  fits well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
  solutes in Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The 
  single particle flux measured by the sFBMcut AD model decays with increasing pore 
  length. The rankings of solute fluxes are consistent with the MSDs predicted by each
  model. We fit the single particle solute flux versus pore length, $L$, to a power law
  function of the form $AL^{-\beta}$ (dashed lines in (b) and (c)). 
  }\label{fig:flux_curves}
  \end{figure}

  % BJC: could use better color scheme. Maybe outline hurst parameters
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{c_parameters.pdf}
%  \caption{}\label{fig:c_parameters}
%  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{beta_parameters.pdf}
%  \caption{}\label{fig:beta_parameters}
%  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
%  \caption{}\label{fig:mfpt_curves}
%  \end{subfigure}
  %BJC: going out to 3 decimal places seems silly
  %BJC: might get closer to beta=2 if I use different curve fitting technique than fitting line to log-log
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{flux_curves_brownian.pdf}
%  \caption{Fixed $H=0.5$}\label{fig:flux_curves_brownian}
%  \end{subfigure}
%  \begin{subfigure}{0.475\textwidth}
%  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
%  \caption{}\label{fig:mfpt_curves_brownian}
%  \end{subfigure}
  %MRS5: the b) pane is a little messy.  If c) is moved to the supporting, maybe can make b into two figures, and 
  % have each just show 1 point?

@@

  The scaling of solute flux with pore length is primarily influenced by anti-correlation
  between solute hops. In Figure~\ref{fig:beta}a, we show that $\beta$, as derived 
  from the sFBMcut model, is inversely related to the Hurst parameter. 
  % BJC6: I'm not sure this sentence adds anything
  %MRS7: reminding people the physics behind models can be useful, though, maybe put back in?
  %This makes intuitive sense since higher degrees of anti-correlation should slow the rate at which solutes
  %cross the membrane pore. 
  $\beta$, as derived from the MSDDM, appears approximately constant which is 
  consistent with nearly invariant transitional Hurst parameters (see 
  Figure~\ref{fig:H_v_state}). However, Figure~\ref{fig:beta}a does raise
  the question as to why $\beta$ is so much lower than the sFBMcut model. The MSDDM 
  is fundamentally similar to the AD model in that one makes correlated draws 
  from a hop distribution, therefore, we should expect the $\beta$ value of the
  MSDDM to be larger than that of Brownian motion.

  The length dependence of solute flux ($\beta$) for the MSDDM is under-estimated 
  primarily due to innaccuracies in the correlation structure of very long FLM 
  trajectories. To generate the curves in Figure~\ref{fig:flux_curves_msddm}, we 
  needed to correlate 25--1000 times more hops than for the MSD predictions in 
  Figure~\ref{fig:msddm_performance}. To understand the behavior of the MSDDM, we 
  studied the $\beta$ parameter derived from variations on the SFBMcut model 
  (see Figure~\ref{fig:beta}a), since we can generate exact realizations of FBM. 
  First, we removed anti-correlation between hops in the sFBMcut trajectory (set
  $H$=0.5). The $\beta$ parameter drops to values similar to the MSDDM. When we 
  remove hop anti-correlation \textit{and} dwell times between hops (set dwell 
  times equal to 1), effectively simulating Brownian motion, we observe similar 
  $\beta$ parameters. These two variations imply that the $\beta$ parameter is 
  only a function of $H$ and not dependent on dwell times ($\alpha$, $\lambda$) 
  or hop lengths ($\sigma$). In Section~\ref{S-section:beta_estimates} of the 
  Supporting Information we expand on this explanation and show that replacing 
  inexact FLM realizations with exact FBM realizations recovers the pore length
  dependence of solute flux.

  %Although the dwell times are
  %insignificant compared to the AD model (compare Figures~\ref{fig:ad_eyetest} and
  %\ref{fig:msddm_eyetest} for example), we have just shown

>>>>

\documentclass[aps,pre,preprint,groupedaddress]{revtex4-2}
\usepackage{CJK}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}

\DeclareUnicodeCharacter{03C9}{$\omega$}
\usepackage[english]{babel}

@@

@@

@@

  \title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
  with Time Series Modeling}

  \author{Benjamin J. Coscia}
  \author{Michael R. Shirts}

  \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, Colorado 80309, United States}

  \date{\today}

  \begin{abstract}

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores. 
  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time 
  random walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore two variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies two sets of parameters based on the solute's radial distance from the
  closest pore center. Next, we generalize Markov state models, treating the
  configurational state of the system as a Markov process, each
  of which has separate transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. 
  %BJC7: added  
  However, qualitative differences between MD and simulated MSDDM trajectories
  may limit its usefulness. 
  Finally, we demonstrate how one can use our models to estimate flux of a solute
  across a macroscopic-length pore and, based on those quantities, the membrane's selectivity towards each solute.
  This work helps to connect microscopic chemically-dependent solute 
  motions and macroscopic membrane performance.

@@

  \maketitle

  \graphicspath{{./figures/}}

@@

  Highly selective separations membranes are desirable in numerous applications. 
  The ability to efficiently separate ions from saline water sources using membranes 
  has been actively pursued for years in an effort to create potable water for people 
  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  there is a strong interest in creating breathable fabrics which selectively allow 
  passage of water vapor.~\cite{mondloch_destruction_2015}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.5\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water present in the tail region is omitted 
  for clarity.}\label{fig:membrane_structure}
  \end{figure}

%  \begin{figure}
%  \centering
%  \subfloat[\label{fig:monomer_structure}]{%
%  			\includegraphics[width=0.4\textwidth, valign=c]{NaGA3C11.pdf}%
%  			\vphantom{\includegraphics[width=0.5\textwidth, valign=c]{membrane_profile.pdf}}
%  			}\hfill
%  \subfloat[\label{fig:membrane_profile}]{\includegraphics[width=0.5\textwidth, valign=c]{membrane_profile.pdf}}\hfill
%  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
%  hexagonal phase in the presence of water where the carboxylate head groups occupy the
%  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
%  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
%  straight and uniform sized pores. Water present in the tail region is omitted 
%  for clarity.}\label{fig:membrane_structure}
%  \end{figure}

@@

  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form: 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. In this work, we only consider the MSD with respect to
  the solutes' center of mass $z$-coordinate, which is oriented along the pore 
  axis. A value of $\alpha < 1$ indicates a subdiffusive process, while values
  of $\alpha = 1$ and $\alpha > 1$ are characteristic of Brownian and 
  superdiffusive motion respectively.

  %BJC7: added following two paragraphs to clarify our usage of the MSD as a tool. Modified a bit below too  
  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions described in subsequent sections.

  We primarily use the MSD as a tool for calculating the average properties of 
  solute trajectories. We only compare MSDs calculated from MD simulations to 
  those generated from our models. We do not use them to calculate diffusion 
  constants or to relate our simulations to experimental measurements. Therefore
  it is only important that we use a consistent definition for calculating the MSD.
%  This approach is valid if we adhere to a consistent definition for MSD 
%  calculations.

  One can measure MSD in two ways. The ensemble averaged MSD measures 
  displacements with respect to a particle's initial position:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation}
  Fits to the \textit{ensemble} averaged MSD will always reproduce the form of 
  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
  displacements over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd}
  \end{equation}
  where T is the length of the trajectory.

%  For a small number of solute 
%  trajectories, this is a much more statistically robust measure of the 
%  average distance a solute travels over time.

@@

  We chose to analyze just the time-averaged MSD because, compared to the ensemble
  average, it is a more statistically robust measure of the average distance a 
  solute travels over time. The ensemble MSD of only 24 solute trajectories would
  have much higher uncertainties.

%  It may be difficult to calculate  ensemble
%  MSD to estimate $\alpha$ with only 24 solute trajectories.
%  
%  Although theoretically possible, we do not use the 
%  ensemble averaged MSD to calculate $\alpha$ because we can extract the same 
%  parameter with higher precision using the dwell time distributions as described below.

@@

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete intervals dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha$ 
  parameter we calculated by maximizing the likelihood function: 
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of	$t$.~\cite{clauset_power-law_2009}

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. 
  %We cannot observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. A standard way of 
  doing this, with easily estimated paramters, is by adding an exponential 
  cut-off to the power law so the dwell time distribution is now proportional 
  to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model. 
  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  \subsection{Solute Flux and Selectivity}\label{section:mfpt}

@@

  It is computationally infeasible to simulate trajectories long enough that they
  traverse the length of a macroscopic pore. To date, the thinnest H\textsubscript{II}
  LLC membrane synthesized with the monomer in this work was 7$\mu$m thick. Using
  24 cores to simulate trajectory realizations in parallel, it takes on the order 
  of 1 day to simulate 10000 sFBMcut realizations of solutes traversing a 50 nm pore.
  The RAM requirements and performance scales greater than linearly and thus would
  take an infeasible amount of memory and time to simulate transport through a pore
  over 100 times longer. One could improve performance significantly by simulating 
  less trajectories. In Figure~\ref{S-fig:flux_curve_sensitivity} of the Supporting 
  Information, we determined that one can simulate as few as 100 sFBMcut realizations
  in order to parameterize Equation~\ref{eqn:flux_decay}. For better precision, we 
  recommend simulating at least 1000 realizations. However, even with an order of 
  magnitude decrease in number of trajectories, it is still infeasible to simulate
  experimental-length pores.

  We used simulated trajectories which traverse computationally-reasonable length
  pores in order to construct an empirical model which one can use to estimate 
  particle flux for arbitrary length pores. We fit Equation~\ref{eqn:passage_times}
  to the empirical distribution of first passage times in Figure~\ref{fig:fpt_distributions}
  and used the expected value of the analytical equation to calculate flux from 
  Equation~\ref{eqn:hill_relation}. As shown in Figure~\ref{fig:flux_curves_ad}, 
  the flux appears to scale according to a power law of the form:
  \begin{equation}
  J(L) = AL^{-\beta} 
  \label{eqn:flux_decay}
  \end{equation}

  \begin{figure}
  \centering
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{fpt_distributions.pdf}
  \caption{}\label{fig:fpt_distributions}
  \end{subfigure}
  \begin{subfigure}{0.485\textwidth}
  \includegraphics[width=\textwidth]{flux_curves.pdf}
  \caption{}\label{fig:flux_curves_ad}
  \end{subfigure}
  \caption{(a) The distributions of first passage times generated from the sFBMcut model
  fit well to Equation~\ref{eqn:passage_times}. We show similar fits for the remaining
  solutes in Figure~\ref{S-fig:ad_fpt_fits} of the Supporting Information. (b) The 
  single particle flux measured by the sFBMcut AD model decays with increasing pore 
  length. The rankings of solute fluxes are consistent with the MSDs predicted by each
  model. We fit the single particle solute flux versus pore length, $L$, to a power law
  function of the form $AL^{-\beta}$ (dashed lines in (b) and (c)). 
  }\label{fig:flux_curves}
  \end{figure}

@@

  The scaling of solute flux with pore length is primarily influenced by anti-correlation
  between solute hops. In Figure~\ref{fig:beta}a, we show that $\beta$ is inversely 
  related to the Hurst parameter. This makes intuitive sense since higher degrees of
  anti-correlation should slow the rate at which solutes cross the membrane pore. 
  When we remove anti-correlation between hops (set $H$=0.5), the length dependence 
  becomes the same for all solutes, dropping to a value just below 2. This also 
  implies that hop lengths and dwell times do not affect length dependence since 
  each solute exhibits different hopping and trapping behavior yet are all parameterized
  by the same value of $\beta$ when $H$=0.5.
  %BJC7: is above argument enough to get rid of following sentence (and associated bar in the Figure)?
  We further verified this claim by removing hop anti-correlation and setting all 
  dwell times equal to one timestep, effectively simulating Brownian motion.
  The length dependence remains unchanged.

  %BJC6: TODO: add (a), (b), (c) labels
  %BJC7: TODO: optimize figure dimensions
  \begin{figure}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{hurst_beta_variations.pdf}
  \caption*{}\label{fig:beta_hurst}
  \end{subfigure}
  \begin{subfigure}{0.31\textwidth}
  % use c_parameters3.py
  %BJC7: I could plot bars with the MSD of each solute to show that trend is same.
  \includegraphics[width=\textwidth]{c_parameter_comparison.pdf}
  \caption*{}\label{fig:c_parameters}
  \end{subfigure}
  \begin{subfigure}{0.66\textwidth}
%  \vspace{-2em}
%  \vspace{0.5em}
  \includegraphics[width=\textwidth]{c_influence.pdf}
  \caption*{}\label{fig:c_influence}
  \end{subfigure}
  \vspace{-1.5cm}
  \caption{(top) Increased anti-correlation between hops (decreased $H$) appears to 
  increase the length-dependence of solute flux (higher $\beta$) for the sFBMcut model.
  If we remove anti-correlation, by setting $H$=0.5, the length dependence parameter
  drops to a value near 2. When we remove hop anti-correlation and dwell times between
  hops, effectively simulating Brownian motion, the $\beta$ parameter stays near 2. 
  This suggests that $\beta$ does not depend on dwell times (parameterized by $\alpha$
  and $\lambda$). (bottom left) As solute flux increases, the scaling of the flux 
  curves, $A$, increases (compare ranking with Figure~\ref{fig:flux_curves_ad}).
  (bottom right) Physical processes which increase the rate of solute displacement 
  result in larger values of $A$. To test the dependence of $A$ on $\alpha$, $\sigma$, 
  $H$ and $\lambda$, we chose a single set of parameters, representative of solutes
  parameterized by the sFBMcut AD model, and generated realizations of the
  model by varying each parameter independently about the same base parameter set. 
%  Therefore, the middle bars for these four 4 parameters are 
%  generated from the same set of parameters. 
  Decreased dwell times (increased $\alpha$), increased hop lengths (increased 
  $\sigma$), and a lower cut-off to the dwell time distribution (increased $\lambda$)
  lead to increases in $A$. 
  %$A$ responds linearly to increases in $\sigma$ and $\lambda$
  and non-linearly to $\alpha$.
  The data suggests that the $A$ parameters do not depend on hop anti-correlation ($H$).
  }\label{fig:beta}
  \end{figure}
